---
title: "h2"
output: html_document
date: "2024-09-30"
---

```{r setup, include=FALSE}
library(readxl)
library(tidyr)
library(tidyverse)
```

```{r}
MrT <- read_excel("TrashNew.xlsx", sheet = 1, skip = 1, na = c(NA,"",","), range = cell_cols("A:N")) |>
  janitor::clean_names() |>
  drop_na(dumpster) |>
  mutate(sports_balls = as.integer(sports_balls), year = as.double(year), type = "Mr")
MrT
ProfT <- read_excel("TrashNew.xlsx", sheet = 2, skip = 1, na = c(NA,"",","), range = cell_cols("A:M")) |>
  janitor::clean_names() |>
  drop_na(dumpster) |>
  filter(dumpster<119) |>
  mutate(type = "ProfT")
ProfT
GwD <- read_excel("TrashNew.xlsx", sheet = 4, skip = 1, na = c(NA,"",","), range = cell_cols("A:L")) |>
  janitor::clean_names() |>
  drop_na(dumpster) |>
  mutate(type = "Gwynnda")
GwD
combined_df = bind_rows(MrT, ProfT, GwD)
combined_df
summary(combined_df)

```
Professor trash wheel collected a total weight of 216.26 tons. Gwnnyda collected
a total of 18120 cigarette butts in June of 2022.
Short description of data: We have data available of 2014 to 2024 for Mr. Trash
wheel, prof. trash wheel and Gwnnyda. The mean homes powered through all of them
has come out to be 46 houses.


```{r}

results = read_csv("results.csv", skip =2) |>
  janitor::clean_names() 
bakes = read_csv("bakes.csv") |>
  janitor::clean_names() 
progress1 = merge(bakes, results, by = c("baker","series","episode"))
bakers_info = read_csv("bakers.csv") |>
  janitor::clean_names() |>
  separate(baker_name, into = c("baker", "last_name"), sep = " ") |>
  unite(description, last_name, baker_age, baker_occupation,hometown, sep=", ") |>
  select(baker, description)
results910 = read_csv("results.csv", skip =2) |>
  janitor::clean_names() |>
  filter(series>8)

progress = merge(progress1, results910, by=c('baker','series','episode','technical','result'), all=TRUE)
print(progress)

df = merge(bakers_info, progress, by= "baker", all = TRUE)
df
```

```{R}
s510_star = read_csv("results.csv", skip = 2) |>
  janitor::clean_names() |>
  select(baker, series, episode, result) |>
  filter(series>4, result == "STAR BAKER")
```

About star baker- yes there were some surprises. For example, Richard got star baker quite
a few times in his season. Yet, he lost to Nancy who only got it once. Tom in season 7 got
star baker twice but got eliminated soon. In season 10, Steph and Alice did well and got
star breaker a lot of times but David who never got the title won the whole season. This
shows that getting star baker in episodes and winning the series is not strongly
associated. We see that in season 8 the winners and runner ups had gotten the most star
bakers. Generally, we can say that more star bakers is more chance making it to the 
finale.

```{R}
viewers = read_csv("viewers.csv")
viewers
summary(viewers)
```

Average in season 1 = 2.875 while average in season 5 = 10.039